### 2022-04-05 paper/Chapters/Background.tex
Prepare Complete (not final) draft
This draft will be sent of to each of the committee members to read through before the thesis defense.
The PDF has been rendered in "final" mode, so no comments will show through.

small.pdf is a compressed version of the main pdf, with no differences except each of the images have been compressed to 300dpi.

\chapter{Background} % Main chapter title

\label{Chapter2} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

@@

In the age of punch cards and monolithic computers the size of entire rooms, it was expected of a computer to only be capable of serving a single function.
Before the technology could be miniaturized, every single computer had to be specialized for the job at hand.
As time passed and technology progressed, a single computer could be produced that served multiple functions as well as be adaptable programmable to handle new tasks that were not considered when the machine was originally built.
This gave rise to what was known as \enquote{Autonomic Computing}, a system of characteristics that are built into a computer to help it self-manage it's resources and adapt to it's administrator's requirements without the need to be redesigned for it's new purpose \citep{AutonomicComputing}.
Autonomic Computing was designed to combat the exponential complexity crisis that came from the widespread availability of computers in different disciplines, since now anyone who could afford a computer could program it for any purpose.
As new use cases were found for computers in day-to-day life and new technologies were being developed to interface with the world around us, the need for componentization became ever more apparent.
Researchers at IBM knew that the best way to address the looming problem of runaway complexity in computers was to develop a way for the computers to automatically interface with any new components that are installed, and to configure itself to only use what is necessary for the job at hand \citep[p.~43]{AutonomicComputing}.
This allowed hardware and software developers to focus on building their products to work with a common standard rather than having to manually integrate their products with every computer.

Once the idea of modularity began to take hold in the computer industry, attention was turned once again towards specializing individual computers.
Now that a computer's physical footprint can be minified, and peripheral components can be added and removed without a complete reengineering of the device, a single computer can be optimized to handle a single task without the overhead cost of building a monolithic computer \citep{Burbeck2007ComplexityAT}.
Now a computer can be specialized to serve a particular purpose or set of purposes while keeping development time comparatively short.
The world has seen this realized through numerous applications such as cell phones, designed to be user-friendly portable devices, computing clusters, built for high-performance computing, or even internet routers, which are built to be a plug-and-play solution for a problem posed to users of all levels of familiarity with computers.
Without this idea of Autonomic Computing, each of these devices would have to be reengineered from the ground up every time a new use case was developed.

@@

The classical manifestation of a personal computer is the desktop computer.
Known for it's componentization, user repairability, and direct connections to power and the network, desktop computers are the best option for a user looking for a workhorse system.
Pieces of the computer could be bought separately, and single parts could be upgraded or replaced by anyone will a little hardware knowledge.
Even though they aren't very portable, desktop computers allow consumers to access greater processor power for a lower cost compared to portable devices \citep{Meyer20145RS}.
Due to this, a desktop PC is often seen at one's home or place of work hardwired to the wall where it remains unmoving unless it needs upgrading, cleaning, or repairs.
Adding on the fact the desktop is modular, it can be easily customized to fit any user's needs, as well as enable particular parts to be replaced or upgraded without needing to rebuild the entire system.

>>>>

\chapter{Background}

\label{Chapter2}

@@

In the age of punch cards and monolithic computers the size of entire rooms, it was expected of a computer to only be capable of serving a single function.
Before the technology could be miniaturized, every single computer had to be specialized for the job at hand.
As time passed and technology progressed, a single computer could be produced that served multiple functions as well as be adaptable programmable to handle new tasks that were not considered when the machine was originally built.
This gave rise to what was known as \enquote{Autonomic Computing}, a system of characteristics that are built into a computer to help it self-manage it's resources and adapt to it's administrator's requirements without the need to be redesigned for it's new purpose \cite{AutonomicComputing}.
Autonomic Computing was designed to combat the exponential complexity crisis that came from the widespread availability of computers in different disciplines, since now anyone who could afford a computer could program it for any purpose.
As new use cases were found for computers in day-to-day life and new technologies were being developed to interface with the world around us, the need for componentization became ever more apparent.
Researchers at IBM knew that the best way to address the looming problem of runaway complexity in computers was to develop a way for the computers to automatically interface with any new components that are installed, and to configure itself to only use what is necessary for the job at hand \cite{AutonomicComputing}.
This allowed hardware and software developers to focus on building their products to work with a common standard rather than having to manually integrate their products with every computer.

Once the idea of modularity began to take hold in the computer industry, attention was turned once again towards specializing individual computers.
Now that a computer's physical footprint can be minified, and peripheral components can be added and removed without a complete reengineering of the device, a single computer can be optimized to handle a single task without the overhead cost of building a monolithic computer \cite{Burbeck2007ComplexityAT}.
Now a computer can be specialized to serve a particular purpose or set of purposes while keeping development time comparatively short.
The world has seen this realized through numerous applications such as cell phones, designed to be user-friendly portable devices, computing clusters, built for high-performance computing, or even internet routers, which are built to be a plug-and-play solution for a problem posed to users of all levels of familiarity with computers.
Without this idea of Autonomic Computing, each of these devices would have to be reengineered from the ground up every time a new use case was developed.

@@

The classical manifestation of a personal computer is the desktop computer.
Known for it's componentization, user repairability, and direct connections to power and the network, desktop computers are the best option for a user looking for a workhorse system.
Pieces of the computer could be bought separately, and single parts could be upgraded or replaced by anyone will a little hardware knowledge.
Even though they aren't very portable, desktop computers allow consumers to access greater processor power for a lower cost compared to portable devices \cite{Meyer20145RS}.
Due to this, a desktop PC is often seen at one's home or place of work hardwired to the wall where it remains unmoving unless it needs upgrading, cleaning, or repairs.
Adding on the fact the desktop is modular, it can be easily customized to fit any user's needs, as well as enable particular parts to be replaced or upgraded without needing to rebuild the entire system.

### 2022-04-05 paper/Chapters/Hardware.tex
Prepare Complete (not final) draft
This draft will be sent of to each of the committee members to read through before the thesis defense.
The PDF has been rendered in "final" mode, so no comments will show through.

small.pdf is a compressed version of the main pdf, with no differences except each of the images have been compressed to 300dpi.

\chapter{Developing the Hardware} % Main chapter title

\label{Chapter4} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{Figures/kicad/close-ups/hdmi-front}
    \caption{The front side of the PCB}
    \label{fig:HDMICircuitFront}
  \end{subfigure}%
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{Figures/kicad/close-ups/hdmi-back}
    \caption{The back side of the PCB}
    \label{fig:HDMICircuitBack}
  \end{subfigure}%
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{Figures/pcb/crops/hdmi}
    \caption{The physical PCB}
    \label{fig:HDMICircuitReal}
  \end{subfigure}
  \caption{The PCB's HDMI circuit}
  \label{fig:HDMICircuit}
\end{figure}

% While this is the image for the CM4 section, it makes sense to put it here
\begin{figure}[b!]
  \centering
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=.95\linewidth]{Figures/kicad/close-ups/cm4-front}
    \caption{The front side of the PCB}
    \label{fig:CM4CircuitFront}
  \end{subfigure}%
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=.95\linewidth]{Figures/kicad/close-ups/cm4-back}
    \caption{The back side of the PCB}
    \label{fig:CM4CircuitBack}
  \end{subfigure}%
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=.95\linewidth]{Figures/pcb/crops/cm4}
    \caption{The physical PCB}
    \label{fig:CM4CircuitReal}
  \end{subfigure}
  \caption{The circuitry surrounding the CM4's two mezzanine connectors}
  \label{fig:CM4Circuit}
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.75\textwidth,page=3]{Figures/kicad/lathrum_thesis_schematic.pdf}
  \caption[USB Schematic]{Schematic layout for interfacing with the Compute Module 4. Expanded in Appendix \ref{app:pcb_schematic_cm4}}
  \label{fig:pcb_schematic_cm4}
\end{figure}

@@

\todo[inline]{Insert pictures of PCB. Thinking at least one showing the flaws of the first board, another of the completed board}

@@

Once the third board was assembled, the board could be tested in full.
While each part of the board was at least partially functional, there were still issues preventing it from working completely.
In particular, USB devices plugged into any of the ports on the board were able to receive power from the board but were unable to transfer data in either direction.
\todo[inline]{I am currently going through and diagnosing this issue}

>>>>

\chapter{Developing the Hardware}

\label{Chapter4}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{Figures/kicad/close-ups/hdmi-front}
    \caption{The front side of the PCB}
    \label{fig:HDMICircuitFront}
  \end{subfigure}%
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{Figures/kicad/close-ups/hdmi-back}
    \caption{The back side of the PCB}
    \label{fig:HDMICircuitBack}
  \end{subfigure}%
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=1\linewidth]{Figures/pcb/crops/hdmi}
    \caption{The physical PCB}
    \label{fig:HDMICircuitReal}
  \end{subfigure}
  \caption[PCB HDMI Circuit]{The PCB's HDMI circuit}
  \label{fig:HDMICircuit}
\end{figure}

% While this is the image for the CM4 section, it makes sense to put it here
\begin{figure}[b!]
  \centering
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=.95\linewidth]{Figures/kicad/close-ups/cm4-front}
    \caption{The front side of the PCB}
    \label{fig:CM4CircuitFront}
  \end{subfigure}%
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=.95\linewidth]{Figures/kicad/close-ups/cm4-back}
    \caption{The back side of the PCB}
    \label{fig:CM4CircuitBack}
  \end{subfigure}%
  \begin{subfigure}{.33\textwidth}
    \centering
    \includegraphics[width=.95\linewidth]{Figures/pcb/crops/cm4}
    \caption{The physical PCB}
    \label{fig:CM4CircuitReal}
  \end{subfigure}
  \caption[PCB CM4 Circuit]{The circuitry surrounding the CM4's two mezzanine connectors}
  \label{fig:CM4Circuit}
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.75\textwidth,page=3]{Figures/kicad/lathrum_thesis_schematic.pdf}
  \caption[CM4 Schematic]{Schematic layout for interfacing with the Compute Module 4. Expanded in Appendix \ref{app:pcb_schematic_cm4}}
  \label{fig:pcb_schematic_cm4}
\end{figure}

@@

@@

Once the third board was assembled, the board could be tested in full.
While each part of the board was at least partially functional, there were still issues preventing it from working completely.
In particular, USB devices plugged into any of the ports on the board were able to receive power from the board but were unable to transfer data in either direction.
Thankfully, this did not prevent testing of the board from being completed, but it did stop the board from being considered a final complete product.
This board could still be used for testing by connecting peripherals such as the keyboard and mouse through bluetooth and powering the screen through USB.
Figure \ref{fig:AssembledPCB} shows the final assembled board, with the final PCB layouts in Figures \ref{app:pcb_layout_front} and \ref{app:pcb_layout_back}.

### 2022-04-05 paper/main.tex
Start Evaluation section, add graphs
Finish draft of evaluation chapter
Prepare Complete (not final) draft
This draft will be sent of to each of the committee members to read through before the thesis defense.
The PDF has been rendered in "final" mode, so no comments will show through.

small.pdf is a compressed version of the main pdf, with no differences except each of the images have been compressed to 300dpi.

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
% draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
% final, % Uncomment to enable final mode (hide todos)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\usepackage{listings} % Required for the code examples
% Code block settings
\lstdefinelanguage{custombash}{
	morekeywords={sudo,cp,cd,rm,mv,read,mkdir,cmake,make,makepkg,buildarmimg},
	morestring=[b]{"},
	morestring=[b]{'},
	morecomment=[l]{\#},
	morekeywords=[2]{pkgname,pkgver,pkgrel,\$pkgname,\$pkgver,\$pkgrel},
}
\lstdefinelanguage{customhtml}{
	morekeywords={DOCTYPE,html,lang,head,script,body,let},
	morekeywords=[2]{nextColor,document,body},
	morekeywords=[3]{addEventListener,setAttribute},
	morestring=[b]{"},
	morestring=[b]{'},
	morecomment=[l]{\#},
}
\lstdefinestyle{custombash}{
  language=custombash,
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  frame=single,
	numbers=left,
  % xleftmargin=\parindent,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  commentstyle=\itshape\color{green!40!black},
  keywordstyle=\bfseries\color{orange!70!black},
  keywordstyle=[2]\bfseries\color{blue!90!black},
  % identifierstyle=\color{blue},
  stringstyle=\color{orange},
}
\lstdefinestyle{customhtml}{
  language=customhtml,
	morekeywords={uint32_t},
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  frame=single,
  % xleftmargin=\parindent,
	numbers=left,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{blue!80!black},
  keywordstyle=[2]\bfseries\color{teal!80!white},
  keywordstyle=[3]\bfseries\color{orange!70!black},
  commentstyle=\itshape\color{green!40!black},
  % identifierstyle=\color{blue},
  stringstyle=\color{orange},
}
\lstdefinestyle{customc}{
  language=C,
	morekeywords={uint32_t},
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  frame=single,
  % xleftmargin=\parindent,
	numbers=left,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{blue!80!black},
  commentstyle=\itshape\color{green!40!black},
  % identifierstyle=\color{blue},
  stringstyle=\color{orange},
}
\lstset{escapechar=@,style=customc}

@@

\begin{acknowledgements}
	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
	The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
\end{acknowledgements}

@@

\dedicatory{For/Dedicated to/To my\ldots}

>>>>

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
% draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
final, % Uncomment to enable final mode (hide todos)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\usepackage{listings} % Required for the code examples
% Code block settings
\lstdefinelanguage{custombash}{
	morekeywords={sudo,cp,cd,rm,mv,read,mkdir,cmake,make,makepkg,buildarmimg},
	morestring=[b]{"},
	morestring=[b]{'},
	morecomment=[l]{\#},
	morekeywords=[2]{pkgname,pkgver,pkgrel,\$pkgname,\$pkgver,\$pkgrel},
}
\lstdefinelanguage{customhtml}{
	morekeywords={DOCTYPE,html,lang,head,script,body,let},
	morekeywords=[2]{nextColor,document,body},
	morekeywords=[3]{addEventListener,setAttribute},
	morestring=[b]{"},
	morestring=[b]{'},
	morecomment=[l]{\#},
}
\lstdefinestyle{custombash}{
  language=custombash,
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  frame=single,
	numbers=left,
  % xleftmargin=\parindent,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  commentstyle=\itshape\color{green!40!black},
  keywordstyle=\bfseries\color{orange!70!black},
  keywordstyle=[2]\bfseries\color{blue!90!black},
  % identifierstyle=\color{blue},
  stringstyle=\color{orange},
}
\lstdefinestyle{customhtml}{
  language=customhtml,
	morekeywords={uint32_t},
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  frame=single,
  % xleftmargin=\parindent,
	numbers=left,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{blue!80!black},
  keywordstyle=[2]\bfseries\color{teal!80!white},
  keywordstyle=[3]\bfseries\color{orange!70!black},
  commentstyle=\itshape\color{green!40!black},
  % identifierstyle=\color{blue},
  stringstyle=\color{orange},
}
\lstdefinestyle{customc}{
  language=C,
	morekeywords={uint32_t},
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  frame=single,
  % xleftmargin=\parindent,
	numbers=left,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{blue!80!black},
  commentstyle=\itshape\color{green!40!black},
  % identifierstyle=\color{blue},
  stringstyle=\color{orange},
}
\lstdefinestyle{plaintext}{
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  frame=single,
	numbers=none,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
}
\lstset{escapechar=@,style=customc}

\usepackage{pgfplots} % Required for the plots
\usepgfplotslibrary{statistics}
\pgfplotsset{compat=1.8}

@@

\begin{acknowledgements}
	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
	I would like to express my graditude to my thesis director, Dr. Robert Heinrichs, and to each of my committee members, Professor Ruben Acu\~{n}a and Dr. Shawn Jordan, for their help in the development of this thesis.
	Without their guidance, I would not have been able to step so far outside of my comfort zone and learn about so many new topics to make this thesis happen.
	I would also like to thank my friends and family who were always there to bounce ideas off of and inevitably tell me when I was trying to fit too many words into a single section.
\end{acknowledgements}

@@

\dedicatory{For my parents, and their endless support, encouragement, and guidance.}
